Report on Late Winter2013 Production: Image Differencing

### 2013-03-28 W13report.tex
Added Russ figures.

@@

>>>>

\section{Results: Measurement {\bf ANDYB}}

Figure~\ref{fluxerr} provides a mosaic of absolute--value S/N
measurements for the {\tt DiaSources} detected at 5--sigma.  The {\it
  top} panel shows the PSF flux measurements reported in the
postfiltered analysis, while the {\it bottom} panel shows the filtered
flux measurements in the prefiltered analysis.  Both distributions are
strongly peaked at 5--sigma, indicating we are not grossly
mismeasuring fluxes in either case.

@@

\begin{figure}
\begin{center}
\centering{\includegraphics[width=0.9\textwidth]{figures/fluxpost.eps}} \\
\centering{\includegraphics[width=0.9\textwidth]{figures/fluxpre.eps}} \\
\end{center}
\caption{Histograms of measured absolute value of signal--to--noise
  for sources detected at 5--sigma in the best postfiltered ({\it
    top}) and prefiltered ({\it bottom}) data.  In postfiltering, we
  use the PSF flux, while in prefiltering we use the filtered flux
  measurement.  }
\label{fluxerr}
\end{figure}
